### 2014-05-19 inst/vign/taxize_vignette.Rmd
rebuilt vignettes

### About the package

@@

### Quick start

#### First, install `taxize`

@@

#### Resolve taxonomic name

@@

```{r resolvenames, eval=TRUE, cache=FALSE}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp[ , -c(1,4)]
```

@@

```{r synonyms, eval=TRUE, cache=FALSE, message=FALSE, warning=FALSE, comment=NA}
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus")
(tsn <- get_tsn(mynames))
library("plyr")
ldply(tsn, itis_acceptname)
```

#### Retrieve higher taxonomic names

@@

Below are a few examples. When you run these examples in R, you are presented with a command prompt asking for the row that contains the name you would like back; that output is not printed below for brevity. In this example, the search term has many matches. The function returns a data.frame of the matches, and asks for the user to input what row number to accept.

```{r interactive, eval=TRUE, echo=TRUE, cache=FALSE}
get_tsn(searchterm = "Heliastes", searchtype = "sciname")
```

In another example, you can pass in a long character vector of taxonomic names:

```{r interactive_many, eval=TRUE, echo=TRUE, cache=FALSE}
splist <- c("annona cherimola", 'annona muricata', "quercus robur")
get_tsn(searchterm = splist, searchtype = "sciname")
```

#### What taxa are the children of my taxon of interest?

@@

```{r downstream, eval=TRUE, cache=FALSE}
col_downstream(name = "Apis", downto = "Species")[[1]]
```

@@

#### Matching species tables with different taxonomic resolution

>>>>

@@

## Quick start

### Installation

@@

### Resolve taxonomic name

@@

```{r resolvenames, eval=TRUE, cache=FALSE}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp$results[ , -c(1,4)]
```

@@

```{r synonyms, eval=TRUE, cache=FALSE, message=FALSE, warning=FALSE, comment=NA}
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus")
(tsn <- get_tsn(mynames, accepted = FALSE))
library("plyr")
ldply(tsn, itis_acceptname)
```

### Retrieve higher taxonomic names

@@

Below are a few examples. When you run these examples in R, you are presented with a command prompt asking for the row that contains the name you would like back; that output is not printed below for brevity. In this example, the search term has many matches. The function returns a data frame of the matches, and asks for the user to input what row number to accept.

```{r interactive, eval=TRUE, echo=TRUE, cache=FALSE}
get_uid(sciname = "Pinus")
```

In another example, you can pass in a long character vector of taxonomic names (although this one is rather short for demo purposes):

```{r interactive_many, eval=TRUE, echo=TRUE, cache=FALSE}
splist <- c("annona cherimola", 'annona muricata', "quercus robur")
get_tsn(searchterm = splist, searchtype = "scientific")
```

### What taxa are the children of my taxon of interest?

@@

```{r downstream, eval=TRUE, cache=FALSE}
col_downstream(name = "Apis", downto = "Species")
```

@@

### Matching species tables with different taxonomic resolution
